---
title: "An Overview of Brazilian Data Professionals"
format: 
  dashboard:
    embed-resources: false
    nav-buttons: [github]
    github: https://github.com/jfajonathan/dashboard-quarto
logo: images/logo.png
theme:
  - cosmo
  - custom.scss
fig-width: 10
fig-asp: 0.3
params:
  year: "2023"
editor_options: 
  chunk_output_type: console
include-in-header:
  - text: |
     <link rel = "shortcut icon" href = "images/favicon.png" />
---

```{r}
#| label: load librarys
#| warning: false
#| message: false

library(tidyverse)
library(highcharter)
library(bslib)
library(bsicons)
library(shiny)
# source("./functions/functions.r")
none <- params$none

theme_set(theme_minimal(base_size = 24, base_family = "Atkinson Hyperlegible"))
```

```{r}
#| label: data
#| warning: false
#| message: false

data <- readr::read_csv("data/final_data.csv")

```

#  {.sidebar}

This dashboard displays statistics for:

|              |                     |
|--------------|---------------------|
| **DATA HACKERS** | State of Data Brazil |
| **YEAR**    | `{r} params$year`   |

------------------------------------------------------------------------

Between November and December 2023, more than 5,200 professionals participated in the State of Data Brazil survey - the largest annual study on the data job market in Brazil. This research is carried out by the Data Hackers community in collaboration with Bain & Company, and this is the 4th edition of the study, which began in 2019.

------------------------------------------------------------------------
::: {.callout-note collapse="true"}
## License
The data contained in this dashboard has been extracted and displayed solely for academic and non-commercial purposes under the Attribution-NonCommercial 4.0 International (CC BY-NC 4.0) license. All credits related to the dataset are reserved for <a> https://www.datahackers.com.br/. </a>
:::

# Localization {.tabset .tabset-fade}

## Row {height="20%"}
```{r}
#| border-radius: 10px;
bslib::value_box(
  max_height = "150px",
  style = "border-radius: 10px;",
  width = "50%",
  title = "Total Answers",
  theme = "blue",
  value = nrow(data),
  showcase = bsicons::bs_icon("people")
)
``` 

```{r}
#| border-radius: 10px;

not_in_brasil <- data %>% 
  select(P1_G) %>%
  summarise(
    not_in_brasil = nrow(data) - sum(P1_G)
  ) %>% 
  pull(not_in_brasil)

bslib::value_box(
  max_height = "150px",
  style = "border-radius: 10px;",
  width = "50%",
  title = "Not living in Brazil",
  theme = "blue",
  value = not_in_brasil,
  showcase = bsicons::bs_icon("globe-central-south-asia")
)
``` 

## Row {height="40%"}
```{r}
#| label: Answered by State
#| warning: false
#| message: false
#| height: 500
#| width: 100%

dados_estados <- data %>%
    select("Estado" = P1_I) %>%
    mutate(P1_I = str_replace(Estado, ".*\\(([^)]+)\\)$", "\\1")) %>%
    group_by(Estado) %>%
    summarise(
        n = n()
    )

dados_genero <- data %>% select(P1_I,P1_B) %>%
    mutate(
        P1_B = case_when(
            P1_B %in% c("Outro","Prefiro não informar") ~ "Outro/Não informado",
            TRUE ~ P1_B
        )
    ) %>%
    rename(Estado = P1_I) %>%
    table() %>%
    as.data.frame() %>%
    pivot_wider(names_from = P1_B,values_from = Freq)

dados_etnia <- data %>% select(P1_I,P1_C) %>%
    rename(Estado = P1_I) %>%
    mutate(P1_C = case_when(
        P1_C %in% c("Outra","Prefiro não informar") ~ "Outra/Não informada",
        TRUE ~ P1_C
    )) %>%
    table() %>%
    as.data.frame() %>%
    pivot_wider(names_from = P1_C,values_from = Freq)

dados_mapa <- dados_estados %>%
    left_join(dados_genero,by = "Estado") %>%
    left_join(dados_etnia,by = "Estado") 


hcmap("countries/br/br-all", data = dados_mapa, value = "n",
      joinBy = c("hc-a2", "Estado"), name= "<b>State Of Data - Brasil 2023 </b>",
      dataLabels = list(enabled = TRUE),
      tooltip = list(pointFormat = paste0(
          "<style='display: block; font-size: 11px;'> <br> 
          <b>Genero</b> <br> 
           - Masculino: {point.Masculino} <br>
           - Feminino: {point.Feminino} <br> 
           - Outro/Não informado: {point.Outro/Não informado} <br> 
           <b> Etnia</b> <br>
            - Branca: {point.Branca} <br> 
            - Preta: {point.Preta} <br> 
            - Parda: {point.Parda} <br> 
            - Amarela: {point.Amarela} <br> 
            - Indígena: {point.Indígena} <br> 
            - Outro/Não informado: {point.Outra/Não informada} <br> <br>
           <b>Total de Respostas</b> <br>
           {point.value} <br> 
           </style>"))
      ) %>%
  hc_title(text = "Brasil") %>%
  hc_colorAxis(min = 0, max = max(dados_mapa$n)) %>% 
  hc_legend(layout = "vertical", align = "right", valueDecimals = 2)

```